### 2020-03-02 rebuttal/rebuttal.tex

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% END MACROS SECTION%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}
\section*{Response to Reviewer for PONE-D-19-32846 ``Theoretical Investigation of a Genetic Switch for Metabolic Adaptation''}
Kathrin S. Laxhuber,$^{1}$ Muir J. Morrison,$^{2}$ Griffin Chure,$^{3}$ Rob Phillips$^{2, 3, \dagger}$
\vspace{10pt}

\noindent\tiny{$^1$ Department of Chemistry and Applied Biosciences, ETH Zurich, 8093 Zurich, Switzerland,
$^2$ Department of Physics, California Institute of Technology, Pasadena, CA, USA,
$^3$ Division of Biology and Biological Engineering, California Institute of Technology, Pasadena, CA, USA, $^\dagger$ E-mail: \texttt{phillips@pboc.caltech.edu}}

{\Large\textcolor{red}{ToDo: change author list above and at the end, add correct github link (public repo!).}}

\begin{responseSummary}
We thank the editor and reviewer for considering our manuscript and
bringing some important points to our attention. The reviewer's comments
significantly improved our work and inspired us to make very interesting
comparisons between the deterministic and stochastic picture of our
system. Furthermore, as rightly suggested by the reviewer, we have now
added experimental data to the manuscript and expanded the author list
to reflect this. Below, we address the reviewer's concerns one-by-one
and indicate where changes were made either to the main text or the
supporting information. Besides these changes, we made a few small
improvements and corrections to the text that had slipped our attention before. We
believe we have resolved the three issues brought up by the reviewer and
hope our manuscript is now ready for publication in PLOS ONE.
\end{responseSummary}

\subsection*{Reviewer \#1}
\begin{review}
In their manuscript "Theoretical investigation of a genetic switch for
metabolic adaptation", Laxhuber and colleagues present a very nice
theoretical analysis of the behavior of the \emph{E. coli} xapABR system, using
both deterministic and stochastic simulations to demonstrate that the
system can show meaningful and important bistability driven by the
activity of the membrane transporter. In general the work is well done,
and it is technically of high quality, but at present I have two
substantial concerns that I think must be addressed in order for the
paper to live up to its potential.
\end{review}

@@

\begin{response}
We thank the reviewer for their careful reading of our work and are
pleased that their impression of the manuscript is favorable overall.
\end{response}

\begin{review}
My first concern is that while the authors present their deterministic
simulations first, and draw many of their conclusions primarily from
those simulations, it seems to me that the use of such simulations is
contra-indicated by the authors' own findings. As both the number of
XapR molecules and mRNA molecules are small integers (likely 10 or
less), treatment of these species as continuous, deterministic
quantities can never be more than a poor approximation. I find this
troublesome for a couple of reasons. First, the authors still treat
their continuous treatment as an apparently 'good' way to model a
genetic switch like that at work at the xapAB promoter; while I find
their analysis insightful, in the end I cannot support such a
recommendation given the stochasticity intrinsic in the low protein and
mRNA copy numbers present here.
\end{review}

\begin{response}
We agree with the concern of the reviewer that in general, deterministic
approximations of systems with such low copy numbers need to be verified. We do not intend to give the general recommendation that a
continuous treatment alone is usually sufficient, and in order to avoid
this, we added some words of warning in the beginning of our
deterministic as well as our stochastic analysis.

Nevertheless, for our system we did successfully test the concordance of the stochastic simulations and the deterministic model. To make this more apparent, we included some additional comparisons of the two
models. We address these in more detail in our responses below,
but to summarize: we added a bifurcation diagram
(Fig~\ref{bifucation}) which illustrates that the stochastic
distributions track the deterministic fixed points very well,
and we compared the stochastic timescales with the solution of the
deterministic model (Fig~\ref{adaptationtime}) and found excellent
agreement there too.

Even though stochastic fluctuations around the deterministic
trajectories may be large, the stochastic trajectories do still flow to
the fixed points as predicted by the deterministic model.
Hence, the excellent agreement may be surprising or unintuitive at first, but the conclusions we draw from the deterministic phase diagrams turn out to be accurate.

%, except when
%the system is close to either of the bifurcation points in
%Fig~\ref{bifucation}, where it is unsurprising that fluctuations are
%magnified in importance.

Given this concordance, we prefer to start by showing the deterministic case and illustrating our conclusions there before moving on to the stochastic picture. That is because the deterministic phase diagrams have the advantage of providing the reader with a more intuitive understanding of the system than the plots of the results from the stochastic simulation.
\end{response}

@@

\begin{review}
Second, while the authors do technically recapitulate the bistable
behavior of the system in the stochastic version, the bistability seems
based on their description to be quite fragile and not very meaningful,
since it only occurs here for small distances between the lower and
upper fixed points
\end{review}

\begin{response}
We thank the reviewer for bringing this point to our attention, which we
believe to be a misunderstanding that resulted from a poor explanation
in our original text. We believe we have clarified this in the
manuscript, and allow us elaborate here too: Stochastic bimodality occurs
only when two of the three fixed points are close together, or in other
words, when the system is poised ``sufficiently near'' one of the
bifurcation points. This may become clearer when looking at the
bifurcation diagram that we added to our section about hysteresis at the
end of the main text. For convenience, we insert this plot below in
Fig~\ref{bifucation} which addresses what we believe the reviewer is
referring to: only when two of the three fixed points are close do the
stochastic trajectories occupy both fixed points, resulting in
bimodality.

Since this bimodality only occurs for a small region in parameter space,
this actually indicates strong and not fragile bistability. In other
words, the fact that the system does not stochastically ``jump'' to the
other fixed point means that the fixed points are very stable to
stochastic fluctuations. Thus, the switch-like feature is robust:
there are two distinct states that the system can occupy, and only near
the bifurcation points is it likely for stochastic trajectories to
transition between them. Put differently, deterministic bistability does
not need to result in stochastic bimodality, and in fact stochastic
bimodality is contrary to robust bistability.
\end{response}

\begin{figure}[h!]
	\centering
	\includegraphics{Fig10_bifurcation.eps}
	\caption{{\bf Bifurcation diagram showing the hysteresis loop in the stochastic system.}
		The blue line shows the positions of the deterministic fixed points, while the dashed line indicates the instability of the middle one. The orange and yellow points show the mean of the stochastic simulations when started at zero and at the high fixed point, respectively. The positions of the two peaks in the bimodal distributions are indicated by smaller points, connected by dotted lines. To make this clearer, the bimodal distributions themselves are shown in a light color (in a smoothed form). The arrows illustrate the hysteresis loop in the stochastic simulations.}
	\label{bifucation}
\end{figure}

@@

\begin{review}
My recommendation would be that the authors put in some more cautionary words about the applicability of the continuous model, and ideally spend a little more time characterizing the discrete model. in terms of switching times, parameters that give rise to bimodal behavior, effects of incorporating reasonable amounts of transcriptional bursting, etc. Some more direct comparisons of the behavior of the two models in similar ranges of parameters space would also likely be enlightening.
\end{review}

\begin{response}
We hope that we have addressed all these points in our responses above
and shortly summarize here: We put in some cautionary words about the
general usage of continuous models (beginning of sections on deterministic as well as stochastic results) and demonstrated that for our system
and the conclusions we draw, the continuous model is surprisingly appropriate (bifurcation diagram and time evolution, end of results section).
Furthermore, we extended our characterization of the stochastic model as
suggested by investigating the distribution of adaptation/switching
times (end of results section) as well as by incorporating transcriptional bursting in our
simulation (end of section C in S1 Text). The deterministic and stochastic model are now directly
compared (for the same set of parameters) in the bifurcation diagram as
well as in terms of their adaptation/switching times.
\end{response}

@@

\begin{review}
My other major difficulty here is that essentially all of the work is
premised on reference 22, which is 'unpublished data.' This is the only
experimental evidence given for the bistability of xapAB expression,
justification of many of the model parameters, experimentally expected
switching timescales, etc. It is impossible to properly interpret the
present work, either for the purposes of review or from the viewpoint of
an interested reader, without availability of those data, which either
ought to be their own independent publication or ought to be included
with this one.
\end{review}

\begin{response}
With further consideration, we agree with the reviewer that we relied
rather heavily on this unpublished data and that it is therefore
essential to make the experimental data available.
We have opted to include the data with this publication rather than
separately. For this reason, we have added Griffin Chure, Nathan Belliveau, Charlotte Strandkvist, and Kyle Naughton to the author list, who collected or were involved in collecting the data. We have added a new section, ``experimental motivation,'' in
the beginning of the main text which discusses the main features of the
data that are relevant for our model. Furthermore, we added a section on
the materials and experimental methods at the end of S1 Text (section
E).
The raw data is
publicly available at \url{https://github.com/RPGroup-PBoC/mwc_activation/}.
\end{response}

### 2020-03-02 main_text/main_text.tex
Partially included Rob's and Griffin's feedback
Rob: done. Griffin: up to experimental motivation.

	\end{flushleft}
	% Please keep the abstract below 300 words
	\section*{Abstract}
	Membrane transporters carry key metabolites through the cell membrane
	and, from a resource standpoint, are hypothesized to be produced only when necessary. The
	expression of membrane transporters in metabolic pathways is often
	upregulated by the transporter substrate. In \emph{E. coli}, such systems
	include for example the \emph{lacY}, \emph{araFGH}, and \emph{xylFGH} genes,
	which encode for lactose, arabinose, and xylose transporters, respectively.
	As a case study of a minimal system, we build a
	generalizable physical model of the \emph{xapABR} genetic
	circuit, which features a regulatory feedback loop through membrane
	transport (positive feedback) and enzymatic degradation (negative feedback)
	of an inducer. Dynamical systems analysis and stochastic simulations show
	that the membrane transport makes the model system bistable in certain
	parameter regimes. Thus, it serves as a genetic ``on-off'' switch, enabling
	the cell to only produce a set of metabolic enzymes when the corresponding
	metabolite is present in large amounts. We find that the negative feedback
	from the degradation enzyme does not significantly disturb the positive
	feedback from the membrane transporter. We investigate hysteresis in the
	switching and discuss the role of cooperativity and multiple binding sites
	in the model circuit. Fundamentally, this work explores how a stable genetic
	switch for a set of enzymes is obtained from transcriptional auto-activation
	of a membrane transporter through its substrate.

@@

	The key feature of the type of system we investigate is the indirect activation of
	the transporter gene by the transporter substrate, leading to positive
	feedback similar to the aforementioned ``on-off'' switch. An example for
	such an architecture is the \emph{lac} operon, where lactose indirectly
	activates the expression of lactose permease. Other examples in \emph{E.
		coli} include the \emph{araFGH} and \emph{xylFGH} operons, which contain genes for
	arabinose and xylose transporters, respectively. For \emph{lac} and
	\emph{araFGH}, bistability has indeed been observed and attributed to such a
	positive feedback
	loop, for example in the well-known study of Novick and Weiner,
	among other works~\cite{Novick1957,Santillan2008,Ozbudak2004,Narang2008,Choi2008,Fritz2014,Jenkins2017,Siegele1997}.
	A eukaryotic example is the glucose transporter GLUT-2 in liver and
	\textbeta-cells~\cite{Bae2010,Tiedge1991}, though this system is much more
	complex than the following analysis.

@@

	A key element of this mechanism is the presence of a transcription factor
	which is always expressed at a low level (often at copy numbers
	of order $\sim10$) and which binds to the transporter substrate.
	This is resource efficient for the cell, as this low copy number
	transcription factor acts as an ``always on'' sensor to detect
	the substrate, allowing high copy numbers of the membrane transporter
	and its attendant operon to be expressed only when
	their substrate is actually present. The transcription factors
	LacI, AraC, and XylR all appear to fill this
	role~\cite{Novick1957,Santillan2008,Ozbudak2004,Narang2008,Choi2008,Fritz2014,Jenkins2017,Siegele1997,Song1997,Schmidt2015}.

	For our modeling, we focus on the \emph{xapABR} genetic circuit from
	\emph{E. coli} as a case study. It is similar to \emph{lac}, but less
	complex. Instead of lactose, its purpose is to make use of the nucleoside
	xanthosine as an energy source~\cite{Buxton1980,Hammer-Jespersen1980}. The
	circuit is made up of two operons: one that encodes for XapR and another
	that encodes for XapA and XapB. XapR appears to be a transcription factor
	that is induced by xanthosine and activates the \emph{xapAB} promoter,
	in close analogy to AraC, XylR, and also LacI.\footnote{One might object that LacI represses its target operon, while
	XapR, AraC, and XylR activate their target operons. However, the analogy
	we wish to draw is that the qualitative logic of their inducers are all
	identical, i.e., the presence of their respective inducer causes their
	target operon to be transcribed.} The \textit{xapAB} promoter has been suggested to have two binding sites for XapR\cite{Seeger1995},
	but the promoter architecture and function is not yet fully understood. The
	transcription of \emph{xapR} seems to be constitutive and not
	auto-regulated~\cite{Seeger1995}. Structural homology to other transcription
	factors suggests that XapR appears in dimers where one dimer can bind two
	xanthosine molecules~\cite{Joergensen1999}. The protein XapA is a purine
	nucleoside phosphorylase that degrades xanthosine into components (ribose
	and xanthine) that can be fed into metabolic
	pathways~\cite{Buxton1980,Hammer-Jespersen1980}. XapB on the other hand is a
	membrane transporter of xanthosine~\cite{Seeger1995,Norholm2001}.

	Experimentally, we found that the expression level of \emph{xapAB} among
	cells follows a bimodal distribution and that the system seems to be
	bistable (see next section). We aim to understand which of the circuit's
	features are necessary for bistability and investigate its behavior in
	different parameter regimes. After presenting some experimental background on the \emph{xap} genes, we will discuss the
	details of our model. Next, we estimate the free parameters and then present
	the observations we made through phase diagrams, followed by the results
	from stochastic simulations.

	\section*{Experimental motivation} \label{sec:experiment}
	Our work was motivated by the experimental observation of bimodality
	in the \emph{xap} circuit, which is shown in Fig~\ref{fig1:data}. We
	focus on the essential findings here and refer the reader
	to~\nameref{S1_Text} for more experimental details. Briefly, we
	placed a fluorescent reporter under the control of the wild type
	(wt) \emph{xapAB} promoter. This construct was placed in three
	different backgrounds: \textDelta\emph{xapABR},
	\textDelta\emph{xapAB}, and wt. The right panel of
	Fig~\subref{fig1:data}{A} shows that for increasing xanthosine
	concentration, expression in the wt-background increases in a
	switch-like way: it is nearly zero when there is little xanthosine
	(``uninduced state''), but increases drastically when there is more
	(``induced state''). In between, the aforementioned bimodal
	distribution is obtained, where some bacteria are in the uninduced
	expression state and others are induced.

	\begin{figure}%[h!]
		\centering
		\includegraphics[width=1\textwidth]{media/Fig1_data.eps}
		\caption{{\bf Experimental data on the \emph{xap} circuit.}
		(A) The expression of the \emph{xapAB} promoter was measured for
		different extracellular concentrations of xanthosine.
		The right panel shows the wild type circuit while
		on the left the genes \emph{xapABR} and in the middle the genes
		\emph{xapAB} are removed. The wild type circuit behaves like a
		switch. Note that the fluorescence scale of the middle panel
		is not comparable with the other two,
		and also that the chosen xanthosine concentrations are different.
		(B) The fold-change in gene expression upon addition of
		xanthosine for the wt promoter (left panel)
		and for the promoter with only the XapR binding site adjacent
		to the polymerase binding site (right panel).
		Note that the fold-change used here differs from fold-change in,
		e.g.,~\cite{Garcia2011,RazoMejia2018,Chure2019},
		in that no subtraction of autofluorescence was carried out,
		which is adequate for the qualitative comparison
		of these two promoters.
		}
		\label{fig1:data}
	\end{figure}

@@

	\begin{figure}%[h!]
		\centering
		\includegraphics{media/Fig10_bifurcation.eps}
		\caption{{\bf Bifurcation diagram showing the hysteresis loop in the stochastic system.}
			The blue line shows the positions of the deterministic fixed
			points, while the dashed line indicates the instability of
			the middle one. The orange and yellow points show the mean
			of the stochastic simulations when started at zero and at
			the high fixed point, respectively. The positions of the two
			peaks in the bimodal distributions are indicated by smaller
			points, connected by dotted lines. The arrows illustrate the
			hysteresis loop in the stochastic simulations.
			}
		\label{fig10:Bifurcation}
	\end{figure}

@@

	\section*{Acknowledgments}
	Portions of the experiments reported here were carried out at the
	Physiology summer course at the Marine Biological Laboratory in Woods
	Hole, MA, operated by the University of Chicago. We thank Charlotte
	Strandkvist and Kyle Naughton for their work on the project during the
	course. We also Nathan Belliveau for strain creation work and for
	bringing similar systems to our
	attention, Patrick Lenggenhager for his help with \emph{Mathematica} issues, and Jane Kondev and Jin Wang for interesting discussions.
	For assistance with illustrations, we also thank Nigel Orme.
	This work was supported by 1R35 GM118043-01 Maximizing Investigators'
	Research Award (MIRA) (to R.P.), and the Werner Siemens Foundation
	through the Swiss Study Foundation (K.S.L.). This material is based upon
	work supported by the National Science Foundation Graduate Research
	Fellowship under Grant No.\ DGE-1745301 (M.J.M.).

>>>>

	\end{flushleft}
	% Please keep the abstract below 300 words
	\section*{Abstract}
	Membrane transporters carry key metabolites across the cell membrane
	and, from a resource standpoint, are hypothesized to be produced when necessary. The
	expression of membrane transporters in metabolic pathways is often
	upregulated by the transporter substrate. In \emph{E. coli}, such systems
	include for example the \emph{lacY}, \emph{araFGH}, and \emph{xylFGH} genes,
	which encode for lactose, arabinose, and xylose transporters, respectively.
	As a case study of a minimal system, we build a
	generalizable physical model of the \emph{xapABR} genetic
	circuit, which features a regulatory feedback loop via membrane
	transport (positive feedback) and enzymatic degradation (negative feedback)
	of an inducer. Dynamical systems analysis and stochastic simulations show
	that the membrane transport makes the model system bistable in certain
	parameter regimes. Thus, it serves as a genetic ``on-off'' switch, enabling
	the cell to only produce a set of metabolic enzymes when the corresponding
	metabolite is present in large amounts. We find that the negative feedback
	from the degradation enzyme does not significantly disturb the positive
	feedback from the membrane transporter. We investigate hysteresis in the
	switching and discuss the role of cooperativity and multiple binding sites
	in the model circuit. Fundamentally, this work explores how a stable genetic
	switch for a set of enzymes is obtained from transcriptional auto-activation
	of a membrane transporter through its substrate.

@@

	The key feature of the type of system we investigate is the indirect activation of
	the transporter gene by the transporter substrate, leading to positive
	feedback similar to the aforementioned ``on-off'' switch. An example for
	such an architecture is the \emph{lac} operon, where lactose indirectly
	activates the expression of lactose permease. Other examples in \emph{E.
		coli} include the \emph{araFGH} and \emph{xylFGH} operons, which contain genes for
	arabinose and xylose transporters, respectively. For \emph{lac} and
	\emph{araFGH}, bistability has indeed been observed and attributed to such a
	positive feedback
	loop, for example in the well-known study by Novick and Weiner (1957),
	among other works~\cite{Novick1957,Santillan2008,Ozbudak2004,Narang2008,Choi2008,Fritz2014,Jenkins2017,Siegele1997}.
	A eukaryotic example is the glucose transporter GLUT-2 in liver and
	\textbeta-cells~\cite{Bae2010,Tiedge1991}, though this system is much more
	complex than the following analysis.

@@

	A key element of this mechanism is the presence of a transcription factor
	which binds to the transporter substrate and which is often expressed at a low level (often at copy numbers
	of order $\sim10$, \cite{Schmidt2015}).
	This is resource efficient for the cell, as this low copy number
	transcription factor acts as an ``always on'' sensor to detect
	the substrate, allowing high copy numbers of the membrane transporter
	and its attendant operon to be expressed only when
	their substrate is actually present. The transcription factors
	LacI, AraC, and XylR all appear to fill this
	role~\cite{Novick1957,Santillan2008,Ozbudak2004,Narang2008,Choi2008,Fritz2014,Jenkins2017,Siegele1997,Song1997,Schmidt2015}.

	For our modeling, we focus on the \emph{xapABR} genetic circuit from
	\emph{E. coli} as a case study. It is similar to \emph{lac}, but less
	complex. Instead of lactose, its purpose is to make use of the nucleoside
	xanthosine as an energy source~\cite{Buxton1980,Hammer-Jespersen1980}. The
	circuit is made up of two operons: one that encodes for XapR and another
	that encodes for XapA and XapB. XapR is a transcription factor
	that is induced by xanthosine and activates the \emph{xapAB} promoter,
	in close analogy to AraC, XylR, and also LacI.\footnote{One might object that LacI represses its target operon, while
	XapR, AraC, and XylR activate their target operons. However, the analogy
	we wish to draw is that the qualitative logic of their inducers are all
	identical, i.e., the presence of their respective inducer causes their
	target operon to be transcribed.} The \textit{xapAB} promoter has been suggested to have two binding sites for XapR\cite{Seeger1995},
	but the promoter architecture and function is not yet fully understood. The
	transcription of \emph{xapR} seems to be constitutive and not
	auto-regulated~\cite{Seeger1995}. Structural homology to other transcription
	factors suggests that XapR appears in dimers where one dimer can bind two
	xanthosine molecules~\cite{Joergensen1999}. The protein XapA is a purine
	nucleoside phosphorylase that degrades xanthosine into components (ribose
	and xanthine) that can be fed into metabolic
	pathways~\cite{Buxton1980,Hammer-Jespersen1980}. XapB on the other hand is a
	membrane transporter of xanthosine~\cite{Seeger1995,Norholm2001}.

	Experimentally, we found that the expression level of \emph{xapAB} among
	cells is bimodal and that the system seems to be
	bistable (see next section). We aim to understand which of the circuit's
	features are necessary for bistability and investigate its behavior in
	different parameter regimes. After presenting some experimental background on the \emph{xap} genes, we discuss the
	details of our model. Next, we estimate the free parameters and then present
	the observations we made through phase diagrams, followed by the results
	from stochastic simulations.

	\section*{Experimental motivation} \label{sec:experiment}
	Our work was motivated by the experimental observation of bimodality
	in the \emph{xap} circuit, which is shown in Fig~\ref{fig1:data}. We
	focus on the essential findings here and refer the reader
	to~\nameref{S1_Text} for more experimental details. Briefly, we
	placed a fluorescent reporter under the control of the wild type
	(wt) \emph{xapAB} promoter. This construct was placed in three
	different backgrounds: \textDelta\emph{xapABR},
	\textDelta\emph{xapAB}, and wt. The left panel of
	Fig~\subref{fig1:data}{A} shows that for increasing xanthosine
	concentration, expression in the wt-background increases in a
	switch-like way: it is nearly zero when there is little xanthosine
	(``uninduced state''), but increases drastically when there is more
	(``induced state''). In between, the aforementioned bimodal
	distribution is obtained, where some bacteria are in the uninduced
	expression state and others are induced.

	\begin{figure}%[h!]
		\centering
		\includegraphics[width=1\textwidth]{media/Fig1_experiment.eps}
		\caption{{\bf Experimental data on the \emph{xap} circuit.}
		(A) The expression of the \emph{xapAB} promoter was measured for
		different extracellular concentrations of xanthosine.
		The left panel shows the wild type circuit while
	in the middle the genes \emph{xapABR} and on the right the genes
		\emph{xapAB} are removed. The wild type circuit behaves like a
		switch. Note that the fluorescence scale of the middle panel
		is not comparable with the other two,
		and also that the chosen xanthosine concentrations are different.
		(B) shows the fold-change in gene expression upon addition of
		xanthosine for the wt promoter (left panel)
		and for the promoter with only the XapR binding site adjacent
		to the polymerase binding site (right panel).
		Note that the fold-change used here differs from fold-change in,
		e.g.,~\cite{Garcia2011,RazoMejia2018,Chure2019},
		in that no subtraction of autofluorescence was carried out,
		which is adequate for the qualitative comparison
		of these two promoters.
		}
		\label{fig1:data}
	\end{figure}

@@

	\begin{figure}%[h!]
		\centering
		\includegraphics{media/Fig10_bifurcation.eps}
		\caption{{\bf Bifurcation diagram showing the hysteresis loop in the stochastic system.}
			The blue line shows the positions of the deterministic fixed
			points, while the dashed line indicates the instability of
			the middle one. The orange and yellow points show the mean
			of the stochastic simulations when started at zero and at
			the high fixed point, respectively. The positions of the two
			peaks in the bimodal distributions are indicated by smaller
			points, connected by dotted lines. To make this clearer, the
			bimodal distributions themselves are shown in a light color (in a smoothed form). The arrows illustrate the
			hysteresis loop in the stochastic simulations.
			}
		\label{fig10:Bifurcation}
	\end{figure}

@@

	\section*{Acknowledgments}
	We thank Patrick Lenggenhager for his help with \emph{Mathematica} issues, Jane Kondev and Jin Wang for interesting discussions, and Nigel Orme for assistance with illustrations. \textcolor{red}{Portions of the experiments reported here were carried out at the
	Physiology Course at the Marine Biological Laboratory in Woods
	Hole, MA, operated by the University of Chicago.}
	This work was supported by 1R35 GM118043-01 Maximizing Investigators'
	Research Award (MIRA) (to R.P.), and the Werner Siemens Foundation
	through the Swiss Study Foundation (K.S.L.). This material is based upon
	work supported by the National Science Foundation Graduate Research
	Fellowship under Grant No.\ DGE-1745301 (M.J.M.).
